---
title: "Lab 6 Comparing two means"
author: ""
date: "`r Sys.Date()`"
output: github_document
---

Researchers studying the number of electric fish species living in various parts of the Amazon basin were interested in whether the presence of tributaries affected the local number of electric fish species in the main rivers (Fernandes et al. 2004).

They counted the number of electric fish species above and below the entrance point of a major tributary at 12 different river locations.

The data is provided in your GitHub repository.

For each question below, write a sentence answering the question and show the code you used to come up with the answer, if applicable.
```{r}
# load packages -----------------------------------------------------------

library(tidyverse)


# read data ---------------------------------------------------------------

fish <- read_csv("chap12q19ElectricFish.csv")
crabs <- read_csv("chap15q27FiddlerCrabFans.csv")

# put data in tidy format ------------------------------------------------

fish_long <- 
  pivot_longer(fish, speciesUpstream:speciesDownstream,
               names_to = "location",
               values_to = "species") %>% 
  mutate(location = str_remove(location, c("species"))) %>% 
  print()

```


## Question A

> Test the hypothesis that the tributaries have no effect on the number of species of electric fish.

ANSWER

```{r t-test}
ttest_results <- t.test(formula = species ~ location, data = fish_long)
ttest_results
```



## Question B

> What is the difference in the mean numbers of species between areas upstream and downstream of a tributary? What is the 95% confidence interval of this difference in means?

ANSWER

Mean_difference = 16.41667-14.58333
                =1.83334

### 95% confidence interval of Mean length difference

Upper_limit = -4.587031

Lower_limit = 8.253697



## Question C

> State the assumptions that you had to make to complete parts (A) and (B). Create a graph to assess whether one of those assumptions was met.

ANSWER

Assumptions:

The tributaries have no effect on the number of species of electric fish.

The distribution of the graph was normal



```{r}
fish_long %>% 
  ggplot(aes(x = species)) +
  geom_histogram(
    aes(fill = location), 
    bins = 8, 
    alpha = 0.5, 
    position = "identity"
  ) +
  scale_fill_manual(values = c("darkorange","cyan4")) +
  theme_minimal()
```

## Question D

> Graph the distribution of body temperatures for each crab type

ANSWER

```{r}
crabs %>% 
  ggplot(aes(x = bodyTemperature)) +
  geom_histogram(
    aes(fill = crabType), 
    bins = 15, 
    alpha = 0.5, 
    position = "identity",
    na.rm= TRUE
  ) +
  scale_fill_manual(values = c("darkorange","cyan4","blue","red")) +
  theme_minimal()
```

## Question E

> Does body temperature varies among crab types? State the null and alternative hypothesis, conduct and ANOVA, and interpret the results.

ANSWER

Yes, the body temperature varies among crab types as it can be seen from the distribution graph.

H0: the body temperature is equal among all crab types.

HA: At least one crab's body temperature is different from the others.

```{r}
aov_bodyTemperature_crabType <-
  aov(bodyTemperature ~ crabType, data = crabs)
aov_bodyTemperature_crabType
summary(aov_bodyTemperature_crabType)
```








